\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1.2in]{geometry}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Races}\label{races}

The description of races are typically not crucial to gameplay. Races
are mostly for role-play and worldbuilding purposes, and may be omitted
entirely for certain settings. The core system includes three generic
races.

\subsection{Race Generalisation}\label{race-generalisation}

\subsubsection{Characteristics Score
Increase}\label{characteristics-score-increase}

A race may provide a basic increase to characteristic scores. This is
typically in the form of a base increase, (+5, etc.) or as a random
dice-based increase (1d10, etc.)

\subsubsection{Age}\label{age}

The age range of a race indicate the ages during which a member of a
race is typically considered an adult. This can vary between societies
of races, and can be waved by the Game Master depending on the
situation. A player may choose to play an exceptionally young, or old
character, and in those situations, it is the responsibility of the Game
Master to either deny the choice, or balance the character in respect to
the player's choices.

Age is not key to any core game mechanics.

\subsubsection{Speed}\label{speed}

The base speed for humanoid creatures is 10m. Other forms of creatures,
and potentially races, may have different speeds.

\subsubsection{Skill Training}\label{skill-training}

The race will typically provide training in skills.

\subsection{Fégée}\label{fuxe9guxe9e}

\textbf{Characteristics Score Increase:} Gain +15 to CHA and MND or +5
to any three characteristics scores.

\textbf{Age:} Fégée typically mature at around 16 - 19 years old, and
live for up to a century and a half.

\textbf{Fée wisdom:} Gain training in any four MND or CHA skills.

\subsection{Goule}\label{goule}

\textbf{Characteristics Score Increase:} Gain +20 to TGH and +10 to STR,
MWS, or RWS, or +5 to any three characteristics scores.

\textbf{Age:} Goule typically mature at around 18 - 22 years old, and
live for up to a century.

\textbf{Labour is power:} Gain training in any four STR, MWS, or RWS
skills.

\subsection{Human}\label{human}

\textbf{Characteristics Score Increase:} Gain +20 to any characteristic
or +2 to all characteristics.

\textbf{Age:} Humans typically mature at around 16 - 19 years old, and
live for less than a century.

\textbf{Jack of all trades:} Gain training in any two skills.

\end{document}
