\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1.2in]{geometry}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Classes}\label{classes}

Classes are key to a character's basic build. They may provide skills,
equipment, and additional features and abilities.

\subsection{Class Generalisation}\label{class-generalisation}

\subsubsection{Skills}\label{skills}

A class will typically provide training in skills.

\subsubsection{Equipment}\label{equipment}

A class will typically provide a set of equipment.

\subsubsection{Class Feature}\label{class-feature}

A class will typically provide a class feature. A class feature is an
ability or bonus available to all users of that class from the
beginning.

\subsection{Channeller}\label{channeller}

\textbf{Skills:} Gain any five skills.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of light armour \emph{or} A dagger.
\item
  A casting item.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +5 in any characteristic.

\subsection{Fighter}\label{fighter}

\textbf{Skills:} Gain four STR, TGH or AGL skills, one MDN or CHA skill,
and one PER skill.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of medium armour \emph{or} One piece of light armour and any
  ranged weapon.
\item
  Any melee weapon and a shield \emph{or} Two melee weapons.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +10 in MWS or RWS.

\subsection{Magician}\label{magician}

\textbf{Skills:} Gain any five skills.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of light armour \emph{or} A dagger.
\item
  A casting item.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +5 in any characteristic.

\subsection{None}\label{none}

\textbf{Skills:} Gain any six skills.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Any weapon.
\item
  Any armour.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +10 in any characteristic.

\subsection{Rogue}\label{rogue}

\textbf{Skills:} Gain two AGL skills, two MDN or CHA skill, and two PER
skill.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of light armour.
\item
  Any light melee weapon \emph{or} Any light ranged weapon.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain training in Sleight of Hand \emph{or}
Stealth \emph{or} +10 in AGL or PER.

\end{document}
