\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1.2in]{geometry}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Spells}\label{spells}

\subsection{Light}\label{light}

\textbf{Level:} 1

\textbf{Mana:} 5

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a small orb of light, roughly
\textasciitilde{}5cm in diameter. The orb gives off around 30 lux.

\subsection{Speed}\label{speed}

\textbf{Level:} 1

\textbf{Mana:} 5

\textbf{Casting time:} Instant

\textbf{Effects:} Infuses a creature with speed. For the next 10
minutes, they move at twice their normal speed.

\subsection{Awareness}\label{awareness}

\textbf{Level:} 1

\textbf{Mana:} 10

\textbf{Casting time:} Instant

\textbf{Effects:} Infuses a creature with increased awareness. For the
next 10 minutes, they gain a +1d10 to checks involving awareness or
perception.

\subsection{Heal}\label{heal}

\textbf{Level:} 1

\textbf{Mana:} 15

\textbf{Casting time:} Instant

\textbf{Effects:} Heals two wounds from any non-mortally injured
location on a creature.

\subsection{Summon Armour}\label{summon-armour}

\textbf{Level:} 3

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Summons a suit of armour. Quality of armour determined
by degrees of success.

\subsection{Explosion}\label{explosion}

\textbf{Level:} 5

\textbf{Mana:} 30

\textbf{Casting time:} Instant

\textbf{Effects:} Creates an explosion with 1d10 meters radius. Deals
damage with DP50 to all creatures within blast radius.

\subsection{Arc Lightning}\label{arc-lightning}

\textbf{Level:} 5

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Create electricity which arcs with ease from living
being to living being. Deals damage with 20DP to all creatures within 5
meters of each other. Conductive objects can be used as a medium to
extend the lightning's reach.

\subsection{Healing Aura}\label{healing-aura}

\textbf{Level:} 2

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Creates an aura with a radius of 10 meters. Heals two
random wounds randomly from all creatures within the aura.

\subsection{Ensnare}\label{ensnare}

\textbf{Level:} 1

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Traps an enemy in pure magical energy for 1d10 turns.
During this time, they cannot take actions, but remain fully conscious.

\subsection{Spark of Anger}\label{spark-of-anger}

\textbf{Level:} 4

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Deals damage with DP10 to the target. Triggers an
enrage, which gives the target an additional +1d10 to all attacks and
damage for 10 turns.

\subsection{Flare}\label{flare}

\textbf{Level:} 2

\textbf{Mana:} 10

\textbf{Casting time:} Instant

\textbf{Effects:} Launches a bright flare in a direction with an initial
velocity of 30 m/s. The flare gives off around 300 lux.

\subsection{Glaciate}\label{glaciate}

\textbf{Level:} 9

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Entombs a creature or object in ice. They are disabled
until it melts.

\subsection{Poison Touch}\label{poison-touch}

\textbf{Level:} 3

\textbf{Mana:} 15

\textbf{Casting time:} Instant

\textbf{Effects:} Infuses a target with poison. They take poison damage
with DP30 each turn for 5 turns.

\subsection{Gravity Well}\label{gravity-well}

\textbf{Level:} 6

\textbf{Mana:} 35

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a gravity well which sucks all objects within
20 meters into it. The gravitational force is equivalent to 0.5g.

\subsection{Ray of Fire}\label{ray-of-fire}

\textbf{Level:} 4

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a beam which lights everything it touches on
fire. It deals damage with DP40 to all creatures hit, and inflicts an
additional DP30 burning damage for 5 turns.

\subsection{Scalding Stream}\label{scalding-stream}

\textbf{Level:} 5

\textbf{Mana:} 30

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a beam of boiling water. Deals damage with
DP60 to all creatures hit, and inflicts an additional DP30 burning
damage for 2 turns.

\subsection{Aggravate}\label{aggravate}

\textbf{Level:} 3

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Triggers enrage, which gives the target an additional
+1d10 to all attacks and damage for 10 turns.

\subsection{Banish to Dust}\label{banish-to-dust}

\textbf{Level:} 4+

\textbf{Mana:} 40

\textbf{Casting time:} 3 turns, Instant

\textbf{Effects:} Disintegrates an object. Size of object depends on
casting level. Cannot target creatures larger than small in size. Can
never target humans.

\subsection{Dimension Gate}\label{dimension-gate}

\textbf{Level:} 12

\textbf{Mana:} 70

\textbf{Casting time:} 6 turns, 10 minutes

\textbf{Effects:} Creates a dimension gate.

\subsection{Portal}\label{portal}

\textbf{Level:} 2

\textbf{Mana:} 35

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a portal to a certain location. The
destination may not be the intended target, depending on the degrees of
failure or success.

\subsection{Hypnosis}\label{hypnosis}

\textbf{Level:} 9

\textbf{Mana:} 40

\textbf{Casting time:} Instant

\textbf{Effects:} The target makes a MND save. On failure, they fall
under the caster's control for 1d10 minutes. Degree of control varies
depending on degrees of failure or success. Cannot be used on the same
person again within 48 hours if failed.

\end{document}
