\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1.2in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{System}\label{system}

\subsection{Game Master}\label{game-master}

The person in charge of the game is known as the Game Master. This
system document assumes you are familiar to traditional tabletop
Role-playing games.

It must be stressed that the Game Master's word is final and absolute.
They are the person in charge of the game, and whatever they say counts
from a rules perspective. There will be parts of the game when a Game
Master's judgement is necessary.

\subsection{System guidelines and
functions}\label{system-guidelines-and-functions}

The system has a broad set of general rules-of-thumb to follow. All the
following rules should be taken as a guideline, and the Game Master's
word may override them.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Specific rules take precedence over general rules. If there are
  contractions, a specific rule should be used over a general one.
\item
  When rounding is necessary, round downwards.
\end{enumerate}

\subsection{Dice}\label{dice}

The base dice used for the system is the \emph{d10}, or a 10-sided dice.
A percentile roll, the \emph{d100}, may be made by using 2d10, treating
the first roll as the value of the tenth digit, and the second roll as
the value of the ones digit.

\subsection{Characteristic scores}\label{characteristic-scores}

Characteristic scores are key to a character's basic construction. They
are an abstraction of a character's basic abilities and characteristics,
of everything from their physical to mental attributes, to weapon
skills.

The following characteristic scores exist.

\subsubsection{Strength}\label{strength}

\emph{Abbreviated as STR.}

\textbf{Strength} is a character's basic ability to achieve physical
feats. These are mostly those that involve feats of strength, such as
lifting, or carrying items, but also include acts such as climbing, and
jumping.

Unarmed melee, and brute melee weapons utilise STR rolls.

\subsubsection{Melee Weapon Strength}\label{melee-weapon-strength}

\emph{Abbreviated as MWS.}

\textbf{Melee weapon strength} represents a character's familiarity, and
proficiency in utilising complex melee weapons.

All non-unarmed, and brute melee weapons utilise MWS rolls.

\subsubsection{Agility}\label{agility}

\emph{Abbreviated as AGL.}

\textbf{Agility} represents a character's dexterity, physical
flexibility, and nimbleness. A character's initiative is also determined
by AGL.

Unarmed ranged weapons utilise AGL rolls.

\subsubsection{Ranged Weapon Strength}\label{ranged-weapon-strength}

\emph{Abbreviated as RWS.}

\textbf{Ranged weapon strength} represents a character's familiarity,
and proficiency in utilising complex ranged weapons.

All non-unarmed ranged weapons utilise RWS rolls.

\subsubsection{Toughness}\label{toughness}

\emph{Abbreviated as TGH.}

\textbf{Toughness} represents a character's physical resilience and
natural defence capabilities. This covers a wide range of different
situations, from resisting status effects such as poison, to retaining
consciousness after sustaining damage, to surviving when potentially
lethal damage is taken.

\subsubsection{Mind}\label{mind}

\emph{Abbreviated as MND.}

\textbf{Mind} is a abstraction of mental processes and abilities. It
covers a character's intelligence, their ability to process and retain
information, and their mental capacity and willpower. MND is also used
when resisting mental status effects, and to resist damage to memory or
mental functions.

\subsubsection{Charisma}\label{charisma}

\emph{Abbreviated as CHA.}

\textbf{Charisma} is a character's ability to charm and coerce. This may
be derived from an innate ability to manipulate, but may involve other
characteristics, including a character's physical attractiveness, and a
character's ability to speak.

\subsubsection{Perception}\label{perception}

\emph{Abbreviated as PER.}

\textbf{Perception} is a character's ability to notice and perceive
their surroundings. This include complex uses of senses, the ability to
detect small details, and the ability to passively, and actively detect
other characters' actions.

\subsection{Degrees of Success and
Failure}\label{degrees-of-success-and-failure}

A single degree of success is counted for every ten a d100 roll beats a
base difficulty. For example, if a check difficulty was 50, and the d100
roll was 30, we would say that roll had 2 degrees of success.

The degree of failure is similar, but counts every ten a d100 roll is
above a base difficulty. If a check difficulty was 50, and the d100 roll
was 72, we would say that roll had 2 degrees of failure.

\subsection{Checks}\label{checks}

Checks are split into two major types.

\subsubsection{Basic Checks}\label{basic-checks}

All basic checks are made in a similar fashion. In order to make a
check, first determine a the check's difficulty. A basic, challenging
difficulty check is equal to the character's relevant characteristic
point.

The following chart may be used to help determine the difficulty of
checks. Please note modifiers are applied to the difficulty of the
check, not the roll.

\begin{longtable}[]{@{}ll@{}}
\toprule
Difficulty & Modifier\tabularnewline
\midrule
\endhead
Trivial & +40\tabularnewline
Simple & +30\tabularnewline
Routine & +20\tabularnewline
Standard & +10\tabularnewline
Challenging & 0\tabularnewline
Hard & -10\tabularnewline
Very Hard & -20\tabularnewline
Painstaking & -30\tabularnewline
Impossible & -40\tabularnewline
\bottomrule
\end{longtable}

After a difficulty has been determined, roll a d100 and compare the roll
to the difficulty. If the roll is lower than the difficulty, the check
succeeds.

\subsubsection{Skill Checks}\label{skill-checks}

\textbf{Skill checks} are made when a character utilises a known skill.
Making a skill check is the same as making a basic check.

\subsubsection{Characteristic Checks}\label{characteristic-checks}

\textbf{Characteristic checks} are made using the base characteristic of
a character. The mechanics for characteristic checks vary depending on
the situation.

\paragraph{Untrained skill checks}\label{untrained-skill-checks}

Untrained skill checks are made when a character does not possess a
skill, but wishes to make a check untrained. In these circumstances, the
rules are the same for making a trained skill check, but all modifies
receive an additional -10.

\begin{longtable}[]{@{}ll@{}}
\toprule
Difficulty & Modifier\tabularnewline
\midrule
\endhead
Trivial & +30\tabularnewline
Simple & +20\tabularnewline
Routine & +10\tabularnewline
Standard & 0\tabularnewline
Challenging & -10\tabularnewline
Hard & -20\tabularnewline
Very Hard & -30\tabularnewline
Painstaking & -40\tabularnewline
Impossible & -50\tabularnewline
\bottomrule
\end{longtable}

\paragraph{Other Characteristic
Checks}\label{other-characteristic-checks}

Characteristic checks are also made in other situations, such as when
resisting status effects, rolling in combat, and most other
circumstances when skills do not apply. Making these checks is the same
as making a basic check.

\subsubsection{Opposing Checks}\label{opposing-checks}

An opposing check is made when a character uses a skill or
characteristic against another character. In these situations, a basic
check is made for both characters with the applicable modifiers. The
character with the least degrees of failure, or the most degrees of
success wins.

In an opposing check, it is impossible for both parties to fail, or
succeed. \# Combat

Combat is designed to be challenging and deadly. It utilises a damage
model based on wounds, rather than hit points.

\subsection{Damage System}\label{damage-system}

\subsubsection{Wounds}\label{wounds}

Each location tracks wounds. Bodily locations include:

\begin{itemize}
\tightlist
\item
  Head
\item
  Right arm
\item
  Left arm
\item
  Torso
\item
  Right leg
\item
  Left leg
\end{itemize}

Each location may sustain three types of damage.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Flesh-wounds:} A hit that results in no immediate danger.
  However, they can build up. Three flesh-wounds create an injury.
\item
  \textbf{Injury:} A strike that is damaging. Each injury on a location
  grants a -5 modifier to utilising that location.
\item
  \textbf{Critical Injury:} An injury that disables the location
  entirely. If this is to the head or torso, it creates a mortal injury.

  \begin{itemize}
  \tightlist
  \item
    Upon receiving a critical injury, make a TGN check. On failure, the
    location is removed. This does not apply to the head or torso.
  \item
    The number of injuries to each location needed to form a Critical
    Injury on a normal human, or human-like creature:

    \begin{itemize}
    \tightlist
    \item
      Arms: 10
    \item
      Legs: 10
    \item
      Head: 5
    \item
      Torso: 20
    \end{itemize}
  \end{itemize}
\end{enumerate}

\subsubsection{Mortal Damage}\label{mortal-damage}

Once a character receives a mortal injury, they become unable to
function. If they are not stabilised within two turns, they must start
rolling toughness checks every turn. If at any point they fail this
check, they die.

\subsubsection{Weapons}\label{weapons}

Each weapon possesses a percentile chance of inflicting an injury. This
is represented by a weapon's DP, or Damage Percentile. If a roll for
damage beats (comes below) this value, an injury is inflicted.

If the roll for damage fails, a flesh-wound is inflicted instead.

If the roll surpasses four degrees of success, it automatically inflicts
a critical injury.

\subsubsection{Armour}\label{armour}

Armour is available for each location. A piece of armour will possess an
armour modifier. The armour modifier is added to the difficulty when
rolling to hit.

\subsubsection{Locational Damage}\label{locational-damage}

\begin{longtable}[]{@{}ll@{}}
\toprule
Region & Dice\tabularnewline
\midrule
\endhead
Head & 1-10\tabularnewline
Right arm & 11-20\tabularnewline
Left arm & 21-30\tabularnewline
Torso & 31-70\tabularnewline
Right leg & 71-85\tabularnewline
Left leg & 86-00\tabularnewline
\bottomrule
\end{longtable}

\subsection{Modifiers}\label{modifiers}

\subsubsection{Status Effects}\label{status-effects}

Status effects are additional effects applied onto characters. These
effects may be beneficial, or negative.

\begin{itemize}
\tightlist
\item
  Blindness
\item
  Charmed
\item
  Deafness
\item
  Fatigue
\item
  Fright
\item
  Incapacitation
\item
  Inspiration
\item
  Paralysis
\item
  Poison
\item
  Rush
\item
  Stun
\end{itemize}

\subsection{Combat Flow}\label{combat-flow}

\subsubsection{Initiating Combat}\label{initiating-combat}

When initiating combat, all character should roll initiative equal to
(x)d10, where x is equal to the tenth digit of the AGL score.

If the attack is unexpected by the defenders, each attacker receives (in
arbitrary order) one extra full turn before initiative is taken into
account.

\subsubsection{Turn actions}\label{turn-actions}

Turns are comprised of two actions. Unless otherwise specified, a
non-movement action immediately ends the turn.

\begin{itemize}
\tightlist
\item
  \textbf{Move:}

  \begin{itemize}
  \tightlist
  \item
    Move within the movement speed of the character.
  \end{itemize}
\item
  \textbf{Sprint:}

  \begin{itemize}
  \tightlist
  \item
    Move twice the movement speed of the character. This ends the turn.
  \end{itemize}
\item
  \textbf{Defend:}

  \begin{itemize}
  \tightlist
  \item
    Defend against the next attack. An attack the following turn has a
    -10 to hitting the defender.
  \end{itemize}
\item
  \textbf{Ranged / Melee Attack:}

  \begin{itemize}
  \tightlist
  \item
    Make the appropriate roll (MWS or RWS) to hit the enemy. The
    attacker may choose to make an aimed shot at a -20 to hit.
  \item
    Roll a d100 to determine the location hit. Refer to Locational
    Damage for chart.
  \item
    On success, make a roll against the weapon's DP.
  \item
    Repeat roll to hit and damage for each attack(s) per action.
  \end{itemize}
\item
  \textbf{Magic Attack:}

  \begin{itemize}
  \tightlist
  \item
    Make a magic roll based on the type of magic user.
  \item
    On success, apply spell effects to target. The target may make an
    agility roll to dodge (MOD -20) if their AGL score is above 30.
  \end{itemize}
\item
  \textbf{Other Actions:}

  \begin{itemize}
  \tightlist
  \item
    Use any other action that may be used outside of combat.
  \end{itemize}
\end{itemize}

\section{Races}\label{races}

The description of races are typically not crucial to gameplay. Races
are mostly for role-play and worldbuilding purposes, and may be omitted
entirely for certain settings. The core system includes three generic
races.

\subsection{Race Generalisation}\label{race-generalisation}

\subsubsection{Characteristics Score
Increase}\label{characteristics-score-increase}

A race may provide a basic increase to characteristic scores. This is
typically in the form of a base increase, (+5, etc.) or as a random
dice-based increase (1d10, etc.)

\subsubsection{Age}\label{age}

The age range of a race indicate the ages during which a member of a
race is typically considered an adult. This can vary between societies
of races, and can be waved by the Game Master depending on the
situation. A player may choose to play an exceptionally young, or old
character, and in those situations, it is the responsibility of the Game
Master to either deny the choice, or balance the character in respect to
the player's choices.

Age is not key to any core game mechanics.

\subsubsection{Speed}\label{speed}

The base speed for humanoid creatures is 10m. Other forms of creatures,
and potentially races, may have different speeds.

\subsubsection{Skill Training}\label{skill-training}

The race will typically provide training in skills.

\subsection{Fégée}\label{fuxe9guxe9e}

\textbf{Characteristics Score Increase:} Gain +15 to CHA and MND or +5
to any three characteristics scores.

\textbf{Age:} Fégée typically mature at around 16 - 19 years old, and
live for up to a century and a half.

\textbf{Fée wisdom:} Gain training in any four MND or CHA skills.

\subsection{Goule}\label{goule}

\textbf{Characteristics Score Increase:} Gain +20 to TGH and +10 to STR,
MWS, or RWS, or +5 to any three characteristics scores.

\textbf{Age:} Goule typically mature at around 18 - 22 years old, and
live for up to a century.

\textbf{Labour is power:} Gain training in any four STR, MWS, or RWS
skills.

\subsection{Human}\label{human}

\textbf{Characteristics Score Increase:} Gain +20 to any characteristic
or +2 to all characteristics.

\textbf{Age:} Humans typically mature at around 16 - 19 years old, and
live for less than a century.

\textbf{Jack of all trades:} Gain training in any two skills.

\section{Classes}\label{classes}

Classes are key to a character's basic build. They may provide skills,
equipment, and additional features and abilities.

\subsection{Class Generalisation}\label{class-generalisation}

\subsubsection{Skills}\label{skills}

A class will typically provide training in skills.

\subsubsection{Equipment}\label{equipment}

A class will typically provide a set of equipment.

\subsubsection{Class Feature}\label{class-feature}

A class will typically provide a class feature. A class feature is an
ability or bonus available to all users of that class from the
beginning.

\subsection{Channeller}\label{channeller}

\textbf{Skills:} Gain any five skills.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of light armour \emph{or} A dagger.
\item
  A casting item.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +5 in any characteristic.

\subsection{Fighter}\label{fighter}

\textbf{Skills:} Gain four STR, TGH or AGL skills, one MDN or CHA skill,
and one PER skill.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of medium armour \emph{or} One piece of light armour and any
  ranged weapon.
\item
  Any melee weapon and a shield \emph{or} Two melee weapons.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +10 in MWS or RWS.

\subsection{Magician}\label{magician}

\textbf{Skills:} Gain any five skills.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of light armour \emph{or} A dagger.
\item
  A casting item.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +5 in any characteristic.

\subsection{None}\label{none}

\textbf{Skills:} Gain any six skills.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Any weapon.
\item
  Any armour.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain +10 in any characteristic.

\subsection{Rogue}\label{rogue}

\textbf{Skills:} Gain two AGL skills, two MDN or CHA skill, and two PER
skill.

\textbf{Equipment:} Start with the following equipment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One piece of light armour.
\item
  Any light melee weapon \emph{or} Any light ranged weapon.
\item
  A knapsack with additional items and supplies.
\end{enumerate}

\textbf{Class Feature:} Gain training in Sleight of Hand \emph{or}
Stealth \emph{or} +10 in AGL or PER.

\section{Skills}\label{skills-1}

A list of skills in the basic system.

\subsection{STR Skills}\label{str-skills}

\begin{itemize}
\tightlist
\item
  Athletics
\item
  Climb
\item
  Martial Arts
\item
  Smithing
\end{itemize}

\subsection{AGL Skills}\label{agl-skills}

\begin{itemize}
\tightlist
\item
  Acrobatics
\item
  Animal Handling
\item
  Contortion
\item
  Crafting
\item
  Disable Device
\item
  Escape
\item
  Penmanship
\item
  Ride
\item
  Sail
\item
  Sleight of Hand
\item
  Stealth
\item
  Surgery
\item
  Swim
\item
  Tracking
\end{itemize}

\subsection{TGH Skills}\label{tgh-skills}

\begin{itemize}
\tightlist
\item
  Survival
\end{itemize}

\subsection{MND Skills}\label{mnd-skills}

\begin{itemize}
\tightlist
\item
  Appraise
\item
  Arcana
\item
  Artificing
\item
  Bureaucracy
\item
  Business
\item
  Calligraphy
\item
  Culture
\item
  Drawing
\item
  Ecology
\item
  Engineering
\item
  Etiquette
\item
  Forgery
\item
  Geography
\item
  History
\item
  Insight
\item
  Linguistics
\item
  Logic
\item
  Medicine
\item
  Nature
\item
  Paining
\item
  Philosophy
\item
  Politics
\item
  Psychology
\item
  Religion
\item
  Religion
\item
  Statistics
\item
  Strategy
\end{itemize}

\subsection{CHA Skills}\label{cha-skills}

\begin{itemize}
\tightlist
\item
  Barter
\item
  Bluff
\item
  Charm
\item
  Courting
\item
  Deception
\item
  Diplomacy
\item
  Disguise
\item
  Instruction
\item
  Intimidation
\item
  Leadership
\item
  Performance
\item
  Persuasion
\item
  Temptation
\end{itemize}

\subsection{PER Skills}\label{per-skills}

\begin{itemize}
\tightlist
\item
  Deduce Motive
\item
  Detect Trap
\item
  Investigation
\item
  Lip Reading
\item
  Navigation
\end{itemize}

\section{Equipment}\label{equipment-1}

\subsection{Weapon Classification}\label{weapon-classification}

Weapons are classified into a few broad categories. More categories may
be created depending on the needs of the world or story.

\subsubsection{Brute Melee}\label{brute-melee}

\subsubsection{Complex Melee}\label{complex-melee}

\subsubsection{Complex Ranged}\label{complex-ranged}

\subsubsection{Light Melee}\label{light-melee}

\subsubsection{Light Ranged}\label{light-ranged}

\subsubsection{Unarmed Melee}\label{unarmed-melee}

\subsubsection{Unarmed Ranged}\label{unarmed-ranged}

\subsection{Armour Classification}\label{armour-classification}

Armour are classified into a few broad categories. More categories may
be created depending on the needs of the world or story.

\subsubsection{Light}\label{light}

\subsubsection{Medium}\label{medium}

\subsubsection{Heavy}\label{heavy}

\subsubsection{Shields}\label{shields}

\section{Magic}\label{magic}

The core ideas of magic operate on a single system. Magic spells are a
combination of a technique, an aspect, and a form.

\subsection{Techniques}\label{techniques}

\begin{itemize}
\tightlist
\item
  Commanding
\item
  Conjuring
\item
  Illusion*
\item
  Infusion
\item
  Invocation
\item
  Knowledge*
\item
  Mimic*
\item
  Mutation*
\item
  Protection
\end{itemize}

Techniques marked with an asterisk (*) do not need to invoke an aspect.

\subsection{Aspects}\label{aspects}

\begin{itemize}
\tightlist
\item
  Acid
\item
  Air
\item
  Arcane
\item
  Body
\item
  Celestial
\item
  Chaos
\item
  Dark
\item
  Death
\item
  Earth
\item
  Egg
\item
  Electricity
\item
  Fire
\item
  Force
\item
  Ghost
\item
  Glass
\item
  Gravity
\item
  Ice
\item
  Life
\item
  Light
\item
  Metal
\item
  Mind
\item
  Nature
\item
  Order
\item
  Poison
\item
  Sand
\item
  Sleep
\item
  Stone
\item
  Time
\item
  Vision
\item
  Water
\item
  Wood
\end{itemize}

\subsection{Forms}\label{forms}

\begin{itemize}
\tightlist
\item
  Arc
\item
  Aura
\item
  Beam
\item
  Being
\item
  Burst
\item
  Dispel
\item
  Entomb
\item
  Object
\item
  Projectile
\item
  Pure
\item
  Self
\end{itemize}

\subsection{Fluid Magic System}\label{fluid-magic-system}

The fluid magic system is dependent on a dynamic system of difficulty
and exhaustion.

\begin{longtable}[]{@{}ll@{}}
\toprule
Scale & Difficulty\tabularnewline
\midrule
\endhead
Inconsequential & 0\tabularnewline
Minor & 10\tabularnewline
Normal & 15\tabularnewline
Somewhat significant & 30\tabularnewline
Significant & 60\tabularnewline
Grand & 90\tabularnewline
Immense & 120\tabularnewline
Universal & 200\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}ll@{}}
\toprule
Technique & Difficulty\tabularnewline
\midrule
\endhead
Mutation & 10\tabularnewline
Invocation & 10\tabularnewline
Conjuring & 20\tabularnewline
Illusion & 20\tabularnewline
Mimic & 20\tabularnewline
Commanding & 30\tabularnewline
Protection & 30\tabularnewline
Infusion & 30\tabularnewline
Knowledge & 30\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}ll@{}}
\toprule
Level & Modifier\tabularnewline
\midrule
\endhead
Level 1 & +10\tabularnewline
Level 2 & +10\tabularnewline
Level 3 & +20\tabularnewline
Level 4 & 0\tabularnewline
Level 5 & 0\tabularnewline
Level 6 & 0\tabularnewline
Level 7 & 0\tabularnewline
Level 8 & 0\tabularnewline
Level 9 & 0\tabularnewline
Level 10 & 0\tabularnewline
Level 11 & 0\tabularnewline
Level 12 & -10\tabularnewline
Level 13 & -20\tabularnewline
Level 14 & -30\tabularnewline
Level 15 & -40\tabularnewline
Level 16 & -50\tabularnewline
Level 17 & -60\tabularnewline
Level 18 & -70\tabularnewline
Level 19 & -85\tabularnewline
Level 20 & -95\tabularnewline
\bottomrule
\end{longtable}

Level modifiers apply to both exhaustion and difficulty.

In order to calculate difficulty, add the base from the technique and
the scale, and any additional modifiers. A successful cast requires a
d100 roll that is lower than the total difficulty.

Speciality in a technique allows for a -20 to difficulty.

Exhaustion is equal to the difficulty squared divided by 70 (dif\^{}2 /
70) rounded to the nearest five.

Exhaustion decays at a rate of 10/hour.

\subsection{Rigid Magic System}\label{rigid-magic-system}

\subsection{Differences Between
Systems}\label{differences-between-systems}

There are two types of magic systems.

The core difference is that rigid spells allocate magical energy
beforehand, whereas fluid modify magical energy in real time. This is
particularly pertinent in situations when those who use the fluid system
(Channellers) use rigid (Magician) spells.

\section{Spells}\label{spells}

\subsection{Light}\label{light-1}

\textbf{Level:} 1

\textbf{Mana:} 5

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a small orb of light, roughly
\textasciitilde{}5cm in diameter. The orb gives off around 30 lux.

\subsection{Speed}\label{speed-1}

\textbf{Level:} 1

\textbf{Mana:} 5

\textbf{Casting time:} Instant

\textbf{Effects:} Infuses a creature with speed. For the next 10
minutes, they move at twice their normal speed.

\subsection{Awareness}\label{awareness}

\textbf{Level:} 1

\textbf{Mana:} 10

\textbf{Casting time:} Instant

\textbf{Effects:} Infuses a creature with increased awareness. For the
next 10 minutes, they gain a +1d10 to checks involving awareness or
perception.

\subsection{Heal}\label{heal}

\textbf{Level:} 1

\textbf{Mana:} 15

\textbf{Casting time:} Instant

\textbf{Effects:} Heals two wounds from any non-mortally injured
location on a creature.

\subsection{Summon Armour}\label{summon-armour}

\textbf{Level:} 3

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Summons a suit of armour. Quality of armour determined
by degrees of success.

\subsection{Explosion}\label{explosion}

\textbf{Level:} 5

\textbf{Mana:} 30

\textbf{Casting time:} Instant

\textbf{Effects:} Creates an explosion with 1d10 meters radius. Deals
damage with DP50 to all creatures within blast radius.

\subsection{Arc Lightning}\label{arc-lightning}

\textbf{Level:} 5

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Create electricity which arcs with ease from living
being to living being. Deals damage with 20DP to all creatures within 5
meters of each other. Conductive objects can be used as a medium to
extend the lightning's reach.

\subsection{Healing Aura}\label{healing-aura}

\textbf{Level:} 2

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Creates an aura with a radius of 10 meters. Heals two
random wounds randomly from all creatures within the aura.

\subsection{Ensnare}\label{ensnare}

\textbf{Level:} 1

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Traps an enemy in pure magical energy for 1d10 turns.
During this time, they cannot take actions, but remain fully conscious.

\subsection{Spark of Anger}\label{spark-of-anger}

\textbf{Level:} 4

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Deals damage with DP10 to the target. Triggers an
enrage, which gives the target an additional +1d10 to all attacks and
damage for 10 turns.

\subsection{Flare}\label{flare}

\textbf{Level:} 2

\textbf{Mana:} 10

\textbf{Casting time:} Instant

\textbf{Effects:} Launches a bright flare in a direction with an initial
velocity of 30 m/s. The flare gives off around 300 lux.

\subsection{Glaciate}\label{glaciate}

\textbf{Level:} 9

\textbf{Mana:} 20

\textbf{Casting time:} Instant

\textbf{Effects:} Entombs a creature or object in ice. They are disabled
until it melts.

\subsection{Poison Touch}\label{poison-touch}

\textbf{Level:} 3

\textbf{Mana:} 15

\textbf{Casting time:} Instant

\textbf{Effects:} Infuses a target with poison. They take poison damage
with DP30 each turn for 5 turns.

\subsection{Gravity Well}\label{gravity-well}

\textbf{Level:} 6

\textbf{Mana:} 35

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a gravity well which sucks all objects within
20 meters into it. The gravitational force is equivalent to 0.5g.

\subsection{Ray of Fire}\label{ray-of-fire}

\textbf{Level:} 4

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a beam which lights everything it touches on
fire. It deals damage with DP40 to all creatures hit, and inflicts an
additional DP30 burning damage for 5 turns.

\subsection{Scalding Stream}\label{scalding-stream}

\textbf{Level:} 5

\textbf{Mana:} 30

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a beam of boiling water. Deals damage with
DP60 to all creatures hit, and inflicts an additional DP30 burning
damage for 2 turns.

\subsection{Aggravate}\label{aggravate}

\textbf{Level:} 3

\textbf{Mana:} 25

\textbf{Casting time:} Instant

\textbf{Effects:} Triggers enrage, which gives the target an additional
+1d10 to all attacks and damage for 10 turns.

\subsection{Banish to Dust}\label{banish-to-dust}

\textbf{Level:} 4+

\textbf{Mana:} 40

\textbf{Casting time:} 3 turns, Instant

\textbf{Effects:} Disintegrates an object. Size of object depends on
casting level. Cannot target creatures larger than small in size. Can
never target humans.

\subsection{Dimension Gate}\label{dimension-gate}

\textbf{Level:} 12

\textbf{Mana:} 70

\textbf{Casting time:} 6 turns, 10 minutes

\textbf{Effects:} Creates a dimension gate.

\subsection{Portal}\label{portal}

\textbf{Level:} 2

\textbf{Mana:} 35

\textbf{Casting time:} Instant

\textbf{Effects:} Creates a portal to a certain location. The
destination may not be the intended target, depending on the degrees of
failure or success.

\subsection{Hypnosis}\label{hypnosis}

\textbf{Level:} 9

\textbf{Mana:} 40

\textbf{Casting time:} Instant

\textbf{Effects:} The target makes a MND save. On failure, they fall
under the caster's control for 1d10 minutes. Degree of control varies
depending on degrees of failure or success. Cannot be used on the same
person again within 48 hours if failed.

\section{Monsters}\label{monsters}

\end{document}
